Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-09-27 paper/paper.Rmd
expannd on AE discussion to close #17

@@

If we consider only the median point forecast, using the absolute error, we see that the ensemble forecast outperformed the surrogate forecast (`r overall_ae_median[model == "Ensemble", round(Mean, digits = 1)]` vs. `r overall_ae_median[model == "Surrogate", round(Mean, digits = 1)]`) which is comparable on the relative scale to the difference in performance observed using WIS. As when using the weighted interval score if we instead consider the median of the absolute error we see that the difference in performance has reduced indicating a similar skewed score distribution for point forecasts as for the whole predictive distribution (`r overall_ae_median[model == "Ensemble", round(Mean, digits = 1)]` vs. `r overall_ae_median[model == "Surrogate", round(Mean, digits = 1)]`).

>>>>

If we consider only the median point forecast, using the absolute error, we see that the ensemble forecast again outperformed the surrogate forecast (`r overall_ae_median[model == "Ensemble", round(Mean, digits = 1)]` vs. `r overall_ae_median[model == "Surrogate", round(Mean, digits = 1)]`). As when using the weighted interval score if we instead consider the median of the absolute error we see that the difference in performance has reduced indicating a similar skewed score distribution for point forecasts as for the whole predictive distribution (`r overall_ae_median[model == "Ensemble", round(Median, digits = 1)]` vs. `r overall_ae_median[model == "Surrogate", round(Median, digits = 1)]`). Across forecast horizons the same pattern of outperformance holds. However, the difference in relative performance was less than when the full probability distribution was accounted for with this becoming more marked as the forecast horizon increased (Figure \@ref(fig:assemble-eval) c).

@@
